Modalities for Location Virtualization

### 2022-09-20 soundness.tex
+

For the definitions that follow, we need some more terminology about stores.

Next, we must define the relation that ties the physical store to the
\logical store, two concepts that we have informally described earlier
(\sref{sec:logical}). From here on, we write~$\store$ for the physical
store and~$\logicalstore$ for the \logical store.

Equipped with the above definitions, we are now prepared to enter the realm of
Iris and perform the three steps described at the beginning of
\sref{sec:soundness}, that is, define the ghost state, the central invariant,
and the assertions of our .. . We give the definitions first and explain them
afterwards.

\begin{comment}
% fp: this is the beginning of an explanation of ghost state in Iris
%     but it quickly grows too long, even though many aspects are missing.
A ghost memory cell in Iris is a memory cell that does not exist at runtime.
The ownership and the content of a physical memory cell are described via a
points-to predicate such as $\loc\pointsto\val$. Similarly, the ownership and
content of a ghost cell are described by an Iris assertion, usually written
$\ownGhost\gamma{a}$, where $\gamma$ is the name of the ghost cell and $a$ is
its content. Whereas the content of a physical memory cell is a
programming-language value~$\val$, the content of a ghost cell inhabits a
mathematical structure, a \emph{camera}~\cite[\S4.4]{iris}, which the user
chooses when the ghost cell is created. A camera is equipped with a
composition operation~$\cdot$ and the ghost state assertion satisfies the law
$\ownGhost\gamma{a\cdot b} \equiv \ownGhost\gamma{a} \star
\ownGhost\gamma{b}$. Thus, the choice of a suitable camera determines in what
ways the ghost state can be split.

A key Iris idiom involves the use of the \emph{authoritative
  camera}~\cite[\S6.3.3]{iris} together with an Iris invariant.
The elements of the authoritative camera include
\emph{authoritative elements} $\authfull{c}$ and
\emph{fragmentary elements} $\authfrag{b}$.
The composition law is defined in such a way that
there always exists at most one authoritative element
and the composition of all fragmentary elements in existence is
contained in the authoritative element, etc.
\end{comment}
% The predicate gen_heap_interp.
\newcommand{\genheapinterp}[1]{\mathit{Heap}\;#1}
% Our predicate pred (defined in ph.v), expanded.
\newcommand{\pred}[1]{\ownGhost\gammaPred{\authfull{(\mapone\predstore)}}}
% A notation for assigning fraction 1 to every element of \predstore.
\newcommand{\mapone}[1]{1.#1}
% The predicate mapsfrom_exact, expanded.
\newcommand{\mapsfromexact}[3]{
  \ownGhost\gammaPred{\authfrag{\singletonMap{#1}{(#2, #3)}}}
}
% A metavariable for a share.
\newcommand{\sh}{L'}
% The predicate mapsfrom, expanded.
\newcommand{\mapsfromdef}[3]{
  \exists\sh.\;
  \mapsfromexact{#1}{#2}{\sh} \star \pure{\sh \subseteq #3}
}

>>>>

Since our semantics operates right on top of the x86-64 machine state (with Iris terminology, physical store),
we do not need to augment the physical store for more abstract reasoning, consequently, we do not need to come up
with a complicated logical relations that ties the physical store to the
\logical store. 
\begin{definition}[Relation between Physical and \Logical Stores]
\label{def:related}
  Two stores $\store$ and $\logicalstore$ are \emph{related},
  which we write $\related\store\logicalstore$, when
  they have the same domain.
\end{definition}

We already have the physical and logical stores and a simple invariant between them. Now, we can rely on the following Assumption \ref{assumption} from Iris to utilize its logical constructions.
% The predicate gen_heap_interp.
\newcommand{\genheapinterp}[1]{\mathit{Heap}\;#1}
% Our predicate pred (defined in ph.v), expanded.
\newcommand{\pred}[1]{\ownGhost\gammaPred{\authfull{(\mapone\predstore)}}}
% A notation for assigning fraction 1 to every element of \predstore.
\newcommand{\mapone}[1]{1.#1}
% The predicate mapsfrom_exact, expanded.
\newcommand{\mapsfromexact}[3]{
  \ownGhost\gammaPred{\authfrag{\singletonMap{#1}{(#2, #3)}}}
}
% A metavariable for a share.
\newcommand{\sh}{L'}
% The predicate mapsfrom, expanded.
\newcommand{\mapsfromdef}[3]{
  \exists\sh.\;
  \mapsfromexact{#1}{#2}{\sh} \star \pure{\sh \subseteq #3}
}
